Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
typo

\paolo{Se bisogno di spazio, posso accorciare la descrizione.}
\begin{itemize}
 \item The Bayesian approach from \cite{guo2010real}, selecting queries according to {\em restricted uninformed VOI} (ruVOI), an heuristic approximation of value-of-information a query, and performing inference using  TrueSkill$^{TM}$ \cite{HerbrichMG06} (an inference scheme based on expectation propagation \cite{Minka01}).

 \item The Bayesian framework of \cite{viappiani2010optimal}, using Monte Carlo methods for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of diplayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called EUS), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).

>>>>

\paolo{Se bisogno di spazio, posso accorciare la descrizione.}
\begin{itemize}
 \item The Bayesian approach from \cite{guo2010real}, selecting queries according to {\em restricted uninformed VOI} (ruVOI), an heuristic approximation of value-of-information, and performing inference using  TrueSkill$^{TM}$ \cite{HerbrichMG06} (an inference scheme based on expectation propagation \cite{Minka01}).

 \item The Bayesian framework of \cite{viappiani2010optimal} using Monte Carlo methods for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of diplayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called EUS), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).
